On the properties of discs around accreting brown dwarfs

### 2010-05-19 BD_disc/paper.tex
test
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2275 25464f21-6099-402c-b30a-640f1d40d38b

The resulting converged disc structures, as discussed in Section
\ref{seds} are then used to create simulated SEDs. In this section we
explore features in these derived SEDs and link them back to the
physical structures within the disc discussed in Section
\ref{disc_struct}. For analysis purposes our SEDs will comprise
contributions from four main luminosity sources. Firstly, the
accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
luminosity ($L_{*}$), will effectively be combined and provide flux at
the shorter wavelength section of the SED. For our parameter space the
temperature of the photospheres has a range of $~$3000\,K$<T_{\rm
  eff}<$1600\,K, this will comprise flux contributions peaking in the
range, 0.97 to 1.8\,$\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
    acc}}$). The accretion spot temperatures, for typical accretors,
will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range 0.3
to 8.5\,$\mu$m. For the extreme accretors temperatures which can reach
as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The second pair of
luminosity sources are from constituent parts of the circumstellar
disc. The inner edge, ($L_{\rm wall}$), at temperatures of $~$370 to
$~$1500\,K, or flux contributions from $~$1.85 to 7.7\,$\mu$m
\citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and the outer
disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less contributing
flux longward of $~$10\,$\mu$m. As discussed in Section \ref{seds} the
{\sc torus} radiative transfer code tags the photons before they reach
the simulated observer in one of four ways, stellar and thermal,
either direct or scattered. These components allow us to analyse the
contributions from the main flux contributors discussed, i.e. $L_{\rm
  acc}$ and $L_*$ equals stellar scattered or direct, with thermal
emission comprising $L_{\rm wall}$ and $L_{\rm disc}$. Figure
\ref{disc_eg_173} shows a typically accreting BDD system with the
component photon contributions highlighted, with $M_*=0.04M_{\odot}$
at 1 Myr with an areal coverage of 10\%, accretion rate of
\logmdot=$-10$ and rotation period of 0.5
days. The solid black line is the total simulated SED, with the
stellar photons shown as blue lines and the thermal as red. The
scattered and direct contributions are then shown as dashed and solid
lines respectively. The horizontal and vertical dotted lines then show
the approximate ranges of the flux contributions from the (from left
to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
and $L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
$J$, and $K$ photometric bands we have adopted.

>>>>

The resulting converged disc structures, as discussed in Section
\ref{seds} are then used to create simulated SEDs. In this section we
explore features in these derived SEDs and link them back to the
physical structures within the disc discussed in Section
\ref{disc_struct}. For analysis purposes our SEDs will comprise
contributions from four main luminosity sources. Firstly, the
accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
luminosity ($L_{*}$), will effectively be combined and provide flux at
the shorter wavelength section of the SED. For our parameter space the
temperature of the photospheres has a range of $~$3000\,K$<T_{\rm
  eff}<$1600\,K, this will comprise flux contributions peaking in the
range, 0.97 to 1.8\,$\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
    acc}}$). The accretion spot temperatures, for typical accretors,
will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range
0.3 to 8.5\,$\mu$m. For the extreme accretors temperatures which can
reach as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The
second pair of luminosity sources are from constituent parts of the
circumstellar disc. The inner edge, ($L_{\rm wall}$), at temperatures
of $~$370 to $~$1500\,K, or flux contributions from $~$1.85 to
7.7\,$\mu$m \citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and
the outer disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less
contributing flux longward of $~$10\,$\mu$m. Disentangling the
accretion and stellar photospheroc flux becomes difficult as $T_{\rm
  acc} \to T_{\rm eff}$, which for an acretion rate of -9 \logmdot,
occurs at a fractional coverages of 20 and 10\%, for rotation periods
of 5 and 0.5 days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). As
discussed in Section \ref{seds} the {\sc torus} radiative transfer
code tags the photons before they reach the simulated observer in one
of four ways, stellar and thermal, either direct or scattered. These
components allow us to analyse the contributions from the main flux
contributors discussed, i.e. $L_{\rm acc}$ and $L_*$ equals stellar
scattered or direct, with thermal emission comprising $L_{\rm wall}$
and $L_{\rm disc}$. Figure \ref{disc_eg_173} shows a typically
accreting BDD system with the component photon contributions
highlighted, with $M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage
of 10\%, accretion rate of \logmdot=$-10$ and rotation period of 0.5
days. The solid black line is the total simulated SED, with the
stellar photons shown as blue lines and the thermal as red. The
scattered and direct contributions are then shown as dashed and solid
lines respectively. The horizontal and vertical dotted lines then show
the approximate ranges of the flux contributions from the (from left
to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
and $L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
$J$, and $K$ photometric bands we have adopted.
